---
title: "Lab3:EDA"
author: Chi-Erh Chiu
format: html
embed-resources: true
---

## Step 1

```{r}
met <- read.csv("met_all.gz")
```

## Step 2

```{r}
dim(met)
head(met)
tail(met)
```

## Step 3

```{r}
str(met)
```

## Step 4

```{r}
table(met$year)
table(met$day)
table(met$hour)
summary(met$temp)
summary(met$elev)
summary(met$wind.sp)
```

```{r}
met$elev[met$elev == 9999.0] <- NA
summary(met$elev)
```

```{r}
met <- met[met$temp > -40, ]
```

The dataset covers only the year 2019, with consistent coverage across days and hours. Some values (–40°C for temp, 9999 for elevation) were invalid and cleaned. After cleaning, the minimum elevation is –13 m and maximum is 4113 m, which is plausible.

## Step 5

```{r}
met <- met[met$temp > -15, ]
summary(met$temp)
```

removed extreme negative temperatures (≤ –15°C) that were likely erroneous. After filtering, the minimum observed temp is –3°C.

## Step 6

```{r}
elev <- met[met$elev == max(met$elev, na.rm = TRUE), ]
summary(elev)

# Correlations
cor(elev$temp, elev$wind.sp, use="complete")
cor(elev$temp, elev$hour, use="complete")
cor(elev$wind.sp, elev$day, use="complete")
cor(elev$wind.sp, elev$hour, use="complete")
cor(elev$temp, elev$day, use="complete")

```

```{r}
hist(met$elev, breaks=100)
```

```{r}
hist(met$temp)
```

```{r}
hist(met$wind.sp)
```

## Step 7

```{r}
library(leaflet)
library(lubridate)
```

```{r}
leaflet(elev) %>%
  addProviderTiles('OpenStreetMap') %>% 
  addCircles(lat=~lat,lng=~lon, opacity=1, fillOpacity=1, radius=100)
```

## Step 8

```{r}
elev$date <- with(elev, ymd_h(paste(year, month, day, hour, sep= ' ')))
summary(elev$date)
elev <- elev[order(elev$date), ] 
head(elev)
```

```{r}
# par(mfrow=c(2,1))
plot(elev$date, elev$temp, type='l')
plot(elev$date, elev$wind.sp, type='l')
```

```{r}
#install.packages("corrplot")
library(corrplot)
cor_matrix <- cor(met[, c("temp", "wind.sp", "elev", "atm.press", "rh", 
                          "dew.point")], use="complete.obs")
corrplot(cor_matrix, method="color", type="upper", 
         title="Correlation Matrix of Weather Variables", 
         mar=c(0,0,1,0))
```
